To Do List

### 2019-05-22 Papers.Rmd
Add Wei and Dunbrack paper on class imbalance

>>>>

- Wei, Qiong, and Roland L. Dunbrack. “The Role of Balanced Training and Testing Data Sets for Binary Classifiers in Bioinformatics.” PloS One 8, no. 7 (2013): e67863. https://doi.org/10.1371/journal.pone.0067863. - Class imbalance. Intro into the problem, methods for addressing class imbalance. Balanced _training_ set is crucial for the best classifier performance, balanced _test_set also helps to improve the results. AUROC is not sensitive to class imbalance, MCC is. Illustrated on predicting missense mutations.
